\textit{Supplementary materials for:} Fitness tracking reveals task-specific associations between memory, mental health, and exercise

### 2021-10-20 paper/main.tex
finished draft of results section, added timecourse figs to supplement

\newcommand{\devices}{S1}
\newcommand{\frDetail}{S2}
\newcommand{\natDetail}{S3}
\newcommand{\vocabDetail}{S4}
\newcommand{\spatialDetail}{S5}
\newcommand{\fitDists}{S6}
\newcommand{\fitDistgridImmediate}{S7}
\newcommand{\fitScatterImmediate}{S8}
\newcommand{\fitDistgridDelayed}{S9}
\newcommand{\fitScatterDelayed}{S10}
\newcommand{\behBehCorr}{S11}
\newcommand{\fitFitCorr}{S12}
\newcommand{\demDemCorr}{S13}
\newcommand{\allCorr}{S14}

@@

\subsubsection*{Regression-based prediction analyses}
Following our exploratory correlation analyses, we used an analogous
bootstrap procedure to identify subsets of memory-related,
fitness-related, and demographic-related variables that predicted
(non-overlapping) subsets of other variables.  For example, we tested
whether a combination of fitness-related variables could predict a
combination of memory-related variables, and so on.

We used the same bootstrap procedure described above (used in our
exploratory correlation analyses) to generate $N = 10,000$ bootstrapped
data matrices whose rows reflected sampled participants and whose
columns reflected different measured variables.  We used a round-robin
imputation procedure to estimate the values of any missing
features~\citep{Buck60}.  We applied this imputation procedure
independently for each bootstrapped data matrix to prevent data
contamination across iterations.

Next, we fit a series of ridge regression models to the training data.
We grouped variables according to whether they were memory-related,
fitness-related, or demographic-related.  We examined whether
fitness-related and demographic-related features could be used to predict
performance on one or more of the memory tasks.

For each set of predictions, we used a bootstrap procedure to estimate
the stability and reliability of those predictions.  For each bootstrap
iteration, we divided the rows of that iteration's data matrix into
training and test sets.  The assignments of rows to these two sets was
random, subject to the constraint that any duplicated rows in the data
matrix (i.e., reflecting a single participant who had been sampled
multiple times) was always assigned to either the training \textit{or}
the test set--i.e., duplicated rows could not appear in both the
training and the test sets.  The training sets always comprised 75\%
of the data, and the tests sets comprised the remaining 25\% of the
data.

For each bootstrap iteration, we computed the root mean squared
deviation (RMSD) between the predicted and observed values in the
target features of the test dataset.  We defined this as the
\textit{observed} RMSD for that bootstrap iteration.  We also
estimated a null distribution of RMSD values by re-fitting each
iteration's data after randomly permuting the rows of the input data
matrix 
(thereby breaking any
meaningful associations between the input and output features).  Taken
together, this yielded a set of $10,000$ observed RMSD values and $10,000$
null RMSD values.  We assessed the statistical significance
($p$-values) of the observed RMSD values by computing the proportions
of null RMSD values that were less than the observed value.  We also
assessed the significance of the observed regression weights using
$t$-tests to compare the means of the observed versus null
distributions of weights, for each combination of features.

\subsubsection*{Reverse correlation analyses}
We sought to characterize potential associations between the history
of participants' fitness-related activities leading up to the time
they participated in a memory task and their performance on the given
task.  For each fitness-related variable, we constructed a timeseries
matrix whose rows corresponded to timepoints (sampled once per day)
leading up to the day the participant accepted the HIT for our study,
and whose columns corresponded to different participants.  These
matrices often contained missing entries, since different
participants' Fitbit devices tracked fitness-related activities
differently.  For example, participants whose Fitbit devices lacked
heart rate sensors would have missing entries for any heart
rate-related variables.  Or, if a given participant neglected to wear
their fitness tracker on a particular day, the column corresponding to
that participant would have missing entries for that day.

@@

Given a fitness timeseries matrix, $F$, we computed the weighted
average and weighted standard error of the mean of each row of $F$,
where the weights were given by a particular memory-related variable
(row of $M$).  For example, if $F$ contained participants' daily step
counts, we could use any row of $M$ to compute a weighted average
across any participants who contributed step count data on each day.
Choosing a row of $M$ that corresponded to participants' performance
on the naturalistic recall task would mean that participants who
performed better on the naturalistic recall task would contribute more
to the weighted average timeseries of daily step counts.
Specifically, for each row, $t$, of $F$, we computed the weighted
average (across the $S$ participants) as:
\[
\bar{f}(t) = \sum_{s=1}^S \dot{m}(s) F(t, s),
\]
where $\dot{m}$ denotes the normalized min-max scaling of $m$ (the row
of $M$ corresponding to the chosen memory-related variable):
\[
  \dot{m} = \frac{m}{\sum_{s=1}^S \hat{m}(s)},
\]
where
\[
  \hat{m} = \frac{m - \min(m)}{\max(m) - \min(m)}
\]

@@

We wondered about potential links between the different aspects of
participants' data.  For example, if people who exercised in a
particular way also tended to perform better on a given memory task,
this could suggest that either (a) some property intrinsic to participants who
exercised in a particular way might also affect their memory
performance on the given task, and/or (b) particular exercise behaviors
could have a causal impact on memory performance.  We carried out an
exploratory analysis whereby we used a bootstrap-based approach (see
\textit{Exploratory correlation analyses}) to
identify reliable correlations between different aspects of memory
performance (Fig.~\behBehCorr), different aspects of fitness (Fig.~\fitFitCorr), different demographic
attributes (Fig.~\demDemCorr), and correlations between memory
performance, fitness information, and demographic attributes
(Fig.~\allCorr).  Several patterns emerged.  First, we found that
participants' performance on the (within-task) immediate versus delayed memory tests
from the free recall, naturalistic recall, and foreign language
flashcards tasks were positively correlated ($r$s $> 0.25$, $p$s $< 0.003$,
bootstrap corrected).  This suggests that, within each of these tasks,
similar processes or constraints may influence both short term and
long term information retrieval.  We also found reliable across-task correlations
between participants' (immediate and delayed) performance on the free
recall and foreign language flashcards tasks ($r$s $> 0.3$, $p$s $< 0.03$,
bootstrap corrected).

A large number of fitness-related measures displayed reliable
correlations (for a complete report, see Fig.~\fitFitCorr).  For
example, body mass index (BMI) and weight were correlated
($r = 0.91, p < 0.0001$, bootstrap corrected).  Resting heart rate over
the prior week was negatively correlated with recent
low-to-moderate-intensity (``fat burn'') cardiovascular
activity levels ($r = 0.70, p = 0.0004$, bootstrap corrected).
Participants' peak heart rate (averaged over the prior week) were also
negatively correlated with recent increases in step counts and daily
elevation gains ($r\mathrm{s} < -0.26, p\mathrm{s} < 0.03$, boostrap
corrected), where recent changes were defined as the average values
over the seven days leading up to the test day divided by the average
values over the preceding 30 days.  Although several demographic
attributes (Fig.~\demDemCorr) displayed trivial correlations (e.g.,
participants identifying as male never reported identifying as female,
and so on), we also observed a negative correlation between reported
stress and alertness ($r = -0.44, p < 0.0001$, bootstrap corrected), and
positive correlations between the reported clarity of the instructions for all
tasks ($r\mathrm{s} > 0.26, p\mathrm{s} < 0.02$, bootstrap corrected).

We also found reliable correlations between participants' fitness and
demographic measures and their behaviors in different tasks
(for a complete report, see Fig.~\allCorr).  For example, recent
low-to-moderate-intensity (``fat burn'') 
cardiovascular activity was positively
correlated with immediate ($r = 0.38, p = 0.03$) and delayed ($r =
0.38, p = 0.029$) recall on the naturalistic
memory task.  Recent increases in moderate-intensity (``cardio'')
activity over the prior 7 days (relative to the preceding 30 days) was
also positively correlated with immediate naturalistic recall ($r =
0.48, p = 0.003$) and immediate recall on the foreign language
flashcards task ($r = 0.43, p = 0.048$).  Recent high-intensity
(``peak'') activity was positively correlated with performance on the
spatial learning task ($r = 0.34, p < 0.0001$), as were recent increases
in high-intensity activity (prior 7 days versus preceding 30 days; $r
= 0.41, p = 0.01$).

\begin{itemize}
% \item characterizing behaviors (color by quartile and continue the
%   color scheme in later figures-- hue reflects task, shading reflects
%   performance.  white outline means immediate, black outline means delayed)
%   \begin{itemize}
%   \item Free recall (immediate + delayed): pfr, lag-CRP, spc  (color:
%     recall performance).  
%     Figure~\ref{fig:fr_behavioral}.
%     \item Naturalistic recall (immediate + delayed): reproduce a version of the sherlock
%       movie/recall trajectories (color: mean precision).  Figure~\ref{fig:nat_behavioral}.
%     \item Foreign language flashcards (immediate + delayed):
%       p(correct) histogram (color: p(correct)).  Figure~\ref{fig:vocab_behavioral}.
%       \item Spatial learning: mean error by number of shapes (color:
%         intercept and slope of line fit to errors as a function of the number of
%         shapes).  Figure~\ref{fig:spatial_behavioral}.
%       \end{itemize}
%     \item Fitness info (break down by task performance, potentially
%       separately for each task); also separate out recent (raw) and
%       recent versus baseline -- color using same color scheme as
%       behavior figure
%       \begin{itemize}
%       \item activity (steps, zone minutes, floors/elevation)
%       \item resting heart rate
%         \item sleep
%         \end{itemize}
  % \item exploratory analysis (correlations).  Possibly make some sort of scatter matrix or pairplot-- rows/columns:
  %         tasks.  Diagonal: histogram of performance metric for that
  %         task.  Above-diagonal entries: compare performance across
  %         tasks (by subject).  Below-diagonal entries: empty?
  %         density/2d histograms?
  %   \begin{itemize}
  %   \item Memory-memory
  %   \item fitness-fitness
  %   \item survey-survey
  %   \item (fitness + survey)-memory
  %   \end{itemize}
  \item predictive analysis (regressions)
    \begin{itemize}
    \item Predict memory performance on held-out task from other tasks
    \item Predict memory performance on each task using fitness data
      \item Predict memory performance on each task using survey data
      \end{itemize}
    \item Reverse correlations: look at recent changes versus baseline
      trends (color using same scheme as behavior figures).  Possibly 
      \begin{itemize}
      \item Fitness profile that predicts performance on each task (barplots + timelines)
      \item Fitness profile for each survey demographic (barplots + timelines)
        \begin{itemize}
          \item Select out mental health demographics (based on meds, stress levels)
          \end{itemize}
        \end{itemize}
  \end{itemize}

  \section*{Discussion}
  \begin{itemize}
  \item summarize key findings
  \item correlation versus causation
         \item what can vs. can't we know?  we can identify correlations, but not causal direction-- e.g. we cannot know whether exercise \textit{causes} mental changes versus whether people with particular neural profiles might tend to engage in particular exercise behaviors.  that being said, we \textit{can} separate out baseline tendencies (e.g., how people tend to exercise in general) versus recent changes (e.g., how they happened to have exercised prior to the experiment).
  \item related work (exercise/memory, exercise/mental health), what this study adds
    \item future direction: towards customized physical exercise recommendation engine for optimizing mental health and mental fitness
    \end{itemize}

>>>>

\newcommand{\devices}{S1}
\newcommand{\frDetail}{S2}
\newcommand{\natDetail}{S3}
\newcommand{\vocabDetail}{S4}
\newcommand{\spatialDetail}{S5}
\newcommand{\fitDists}{S6}
\newcommand{\fitDistgridImmediate}{S7}
\newcommand{\fitScatterImmediate}{S8}
\newcommand{\fitDistgridDelayed}{S9}
\newcommand{\fitScatterDelayed}{S10}
\newcommand{\behBehCorr}{S11}
\newcommand{\fitFitCorr}{S12}
\newcommand{\demDemCorr}{S13}
\newcommand{\allCorr}{S14}
\newcommand{\activityTimecourse}{S15}
\newcommand{\cardioTimecourse}{S16}
\newcommand{\sleepTimecourse}{S17}
\newcommand{\activityTimecourseMH}{S18}
\newcommand{\cardioTimecourseMH}{S19}
\newcommand{\sleepTimecourseMH}{S20}

@@

\subsubsection*{Reverse correlation analyses}
We sought to characterize potential associations between the history
of participants' fitness-related activities leading up to the time
they participated in a memory task and their performance on the given
task.  For each fitness-related variable, we constructed a timeseries
matrix whose rows corresponded to timepoints (sampled once per day)
leading up to the day the participant accepted the HIT for our study,
and whose columns corresponded to different participants.  These
matrices often contained missing entries, since different
participants' Fitbit devices tracked fitness-related activities
differently.  For example, participants whose Fitbit devices lacked
heart rate sensors would have missing entries for any heart
rate-related variables.  Or, if a given participant neglected to wear
their fitness tracker on a particular day, the column corresponding to
that participant would have missing entries for that day.  To create
stable estimates, we smoothed the timeseries of each fitness measure
using a sliding window of 1 week.  In other words, for each fitness
measure, we replaced the ``observed
value'' for each day with the average values of that measure (when
available) over the 7 day interval ending on the given day.

@@

Given a fitness timeseries matrix, $F$, we computed the weighted
average and weighted standard error of the mean of each row of $F$,
where the weights were given by a particular memory-related variable
(row of $M$).  For example, if $F$ contained participants' daily step
counts, we could use any row of $M$ to compute a weighted average
across any participants who contributed step count data on each day.
Choosing a row of $M$ that corresponded to participants' performance
on the naturalistic recall task would mean that participants who
performed better on the naturalistic recall task would contribute more
to the weighted average timeseries of daily step counts.
Specifically, for each row, $t$, of $F$, we computed the weighted
average (across the $S$ participants) as:
\[
\bar{f}(t) = \sum_{s=1}^S \dot{m}(s) F(t, s),
\]
where $\dot{m}$ denotes the normalized min-max scaling of $m$ (the row
of $M$ corresponding to the chosen memory-related variable):
\[
  \dot{m} = \frac{m}{\sum_{s=1}^S \hat{m}(s)},
\]
where
\[
  \hat{m} = (1 - \epsilon)\frac{m - \min(m)}{\max(m) - \min(m)} + \epsilon.
\]
Here, $\epsilon$ provides a lower bound on the influence of the
lowest-weighted participant's data.  We defined $\epsilon = 0.001$,
ensuring that the lowest-weighted participant had relatively low (but
non-zero) influence.

@@

We wondered about potential links between the different aspects of
participants' data.  For example, if people who exercised in a
particular way also tended to perform better on a given memory task,
this could suggest that either (a) some property intrinsic to participants who
exercised in a particular way might also affect their memory
performance on the given task, and/or (b) particular exercise behaviors
could have a causal impact on memory performance.  We carried out an
exploratory analysis whereby we used a bootstrap-based approach (see
\textit{Exploratory correlation analyses}) to
identify reliable correlations between different aspects of memory
performance (Fig.~\behBehCorr), different aspects of fitness (Fig.~\fitFitCorr), different demographic
attributes (Fig.~\demDemCorr), and correlations between memory
performance, fitness information, and demographic attributes
(Fig.~\allCorr).  Several patterns emerged.  First, we found that
participants' performance on the (within-task) immediate versus delayed memory tests
from the free recall, naturalistic recall, and foreign language
flashcards tasks were positively correlated ($r$s $> 0.25$, $p$s $< 0.003$).  This suggests that, within each of these tasks,
similar processes or constraints may influence both short term and
long term information retrieval.  We also found reliable across-task correlations
between participants' (immediate and delayed) performance on the free
recall and foreign language flashcards tasks ($r$s $> 0.3$, $p$s $< 0.03$).

A large number of fitness-related measures displayed reliable
correlations (for a complete report, see Fig.~\fitFitCorr).  For
example, body mass index (BMI) and weight were correlated
($r = 0.91, p < 0.0001$).  Resting heart rate over
the prior week was negatively correlated with recent
low-to-moderate-intensity (``fat burn'') cardiovascular
activity levels ($r = 0.70, p = 0.0004$).
Participants' peak heart rate (averaged over the prior week) were also
negatively correlated with recent increases in step counts and daily
elevation gains ($r\mathrm{s} < -0.26, p\mathrm{s} < 0.03$, boostrap
corrected), where recent changes were defined as the average values
over the seven days leading up to the test day divided by the average
values over the preceding 30 days.  Although several demographic
attributes (Fig.~\demDemCorr) displayed trivial correlations (e.g.,
participants identifying as male never reported identifying as female,
and so on), we also observed a negative correlation between reported
stress and alertness ($r = -0.44, p < 0.0001$), and
positive correlations between the reported clarity of the instructions for all
tasks ($r\mathrm{s} > 0.26, p\mathrm{s} < 0.02$).

\begin{figure}[tp]
\centering
\includegraphics[width=0.8\textwidth]{figs/corr_MH}
\caption{\textbf{Memory performance differs according to mental health
    measures.}  The reported values in the table reflect correlations
  between each behavioral measure and mental health measure.
  Only statistically reliable correlations ($p < 0.05$, corrected) are displayed. 
  We used participants' mean recall accuracy to characterize
  performance on the free recall and
  foreign language flashcards tasks, and mean precision to
  characterize performance on the naturalistic recall tasks.  We
  characterized performance on the spatial learning task using the
  (inverted and normalized)
  intercepts and slopes of linear regressions on mean estimation
  errors as a function of the number of studied shapes (also see
  Figs.~\ref{fig:immediate_behavior}, \ref{fig:delayed_behavior},
  \frDetail, \natDetail, \vocabDetail, and \spatialDetail).  Typical
  and current stress levels were measured by self report.  Mental
  health information was inferred using each participants' list of
  self-reported medications.}
\label{fig:mh_corr}
\end{figure}

We also found reliable correlations between participants' fitness and
demographic measures and their behaviors in different tasks
(for a complete report, see Fig.~\allCorr).  For example, recent
low-to-moderate-intensity (``fat burn'') 
cardiovascular activity was positively
correlated with immediate ($r = 0.38, p = 0.03$) and delayed ($r =
0.38, p = 0.029$) recall on the naturalistic
memory task.  Recent increases in moderate-intensity (``cardio'')
activity over the prior 7 days (relative to the preceding 30 days) was
also positively correlated with immediate naturalistic recall ($r =
0.48, p = 0.003$) and immediate recall on the foreign language
flashcards task ($r = 0.43, p = 0.048$).  Recent high-intensity
(``peak'') activity was positively correlated with performance on the
spatial learning task ($r = 0.34, p < 0.0001$), as were recent increases
in high-intensity activity (prior 7 days versus preceding 30 days; $r
= 0.41, p = 0.01$).  Mental health indicators, such as self-reported
stress levels and medications were also associated with differences in
memory (Figs.~\ref{fig:mh_corr}, \allCorr).  For example, self-reported stress levels at the time of test
were negatively correlated with performance on the delayed memory test
for the foreign language flashcards task ($r = -0.29, p = 0.038$),
whereas participants who were medicated for anxiety and depression
tended to perform slightly (but reliably) \textit{better} on the immediate memory test for the
foreign language flashcards task ($r = 0.11, p < 0.0001$).

\begin{figure}[tp]
\centering
\includegraphics[width=\textwidth]{figs/weighted_timecourse_summary}
\caption{\textbf{Dynamics of physical activity varies with memory
    performance and mental health measures.}  \textbf{a. Daily step counts.}  Each
  timecourse is weighted by either performance on immediate recall tests
  (left panel) or on delayed recall tests (right panel).  The black
  (baseline) timecourses display the (unweighted) average across all
  participants.  \textbf{b. Daily duration (in minutes) of low-intensity physical
    activity.}  Timecourses are displayed in the same format and color
scheme as those in Panel A.  \textbf{c. Timecourses of physical
  activity, weighted by mental health measures.}  The timecourses in
each panel display the average daily step counts (top panel) or
duration of low-intensity activity (bottom panel).  Each color denotes
the average timecourse for all participants with the indicated
mental health conditions.  The baseline curves (black) display the
average across all participants (re-plotted in Panel C to illustrate
scale differences across panels).  Error ribbons in all panels denote
the standard error of the mean.  Horizontal lines below each panel's
timecourses denote intervals over which each weighted measure (color) differs
from the unweighted baseline.}
\label{fig:dynamics}
\end{figure}

The above analyses indicate that recent differences in fitness-related
activity are associated with differences in memory performance and
mental health measures.  Although the analyses treated these measures
on average or in aggregate, many of the measures we collected are
dynamic. For example, the amount or intensity of physical exercise
people engage in can vary over time, and so on.  We wondered whether
the dynamics of fitness-related measures might related to memory
performance and mental health measures.  To this end, we carried out a
series of reverse correlation analyses (see \textit{Reverse
  correlation analyses}) to examine whether participants with
different cognitive or mental health profiles also tended to display
differences in fitness-related measures over time.  In particular, we
examined fitness data collected from participants' Fitbit devices over
the year prior to their test day in our study.  Several example findings are summarized in
Figure~\ref{fig:dynamics}.  We found that participants who performed
well on the immediate and delayed free recall memory tests and on the
naturalistic recall tests tended to be more active than participants
who performed poorly on those tests (Figs.~\ref{fig:dynamics}a, b;
\activityTimecourse).  Conversely, participants who performed well on
the immediate and delayed foreign language flashcards tasks tended to
be \textit{less} active.  These differences were present even a full
year before the testing day.  We also found substantial variability
across people with different (self-reported) mental health profiles
(Figs.~\ref{fig:dynamics}c, \activityTimecourseMH).  Due to small sample
sizes of individuals exhibiting several mental health dimensions, it
is difficult to distinguish generalizable trends from individual
differences that one or two individuals happened to exhibit.  However,
several large-sample-size trends emerged.  For example, participants
who reported higher levels of stress also tended to be slightly more
physically active than participants who reported lower stress levels.
We found analogous differences in other activity-related measures
(Figs.~\activityTimecourse~and \activityTimecourseMH), cardiovascular
measures (Figs.~\cardioTimecourse~and \cardioTimecourseMH), and
sleep-related measures (Figs.~\sleepTimecourse~and
\sleepTimecourseMH).  Taken together, the analyses suggest that
cogntive and mental health differences are also associated with differences
in the dynamics of physical health measures.

\section*{Discussion}

  \begin{itemize}
  \item summarize key findings
  \item correlation versus causation
         \item what can vs. can't we know?  we can identify correlations, but not causal direction-- e.g. we cannot know whether exercise \textit{causes} mental changes versus whether people with particular neural profiles might tend to engage in particular exercise behaviors.  that being said, we \textit{can} separate out baseline tendencies (e.g., how people tend to exercise in general) versus recent changes (e.g., how they happened to have exercised prior to the experiment).
  \item related work (exercise/memory, exercise/mental health), what this study adds
    \item future direction: towards customized physical exercise recommendation engine for optimizing mental health and mental fitness
    \end{itemize}

### 2021-10-20 paper/supplement.tex
finished draft of results section, added timecourse figs to supplement

\begin{sidewaysfigure}[p]
\centering
\includegraphics[width=\textwidth]{figs/behavior_fitness+survey_correlations}
\caption{\textbf{Bootstrap-estimated reliable correlations between
    behavioral measures and fitness or demographic measures.}}
\label{fig:survey_corrs}
\end{sidewaysfigure}

>>>>

\begin{sidewaysfigure}[p]
\centering
\includegraphics[width=\textwidth]{figs/behavior_fitness+survey_correlations}
\caption{\textbf{Bootstrap-estimated reliable correlations between
    behavioral measures and fitness or demographic measures.}}
\label{fig:fitness_survey_corrs}
\end{sidewaysfigure}

\begin{figure}[p]
  \centering
  \includegraphics[width=0.75\textwidth]{figs/weighted_timecourse_activity}
\caption{\textbf{History of fitness activity levels weighted by
    behavioral performance.}}
\label{fig:activity_timecourse}
\end{figure}

\begin{figure}[p]
  \centering
  \includegraphics[width=0.7\textwidth]{figs/weighted_timecourse_HR}
\caption{\textbf{History of cardiovascular activity weighted by
    behavioral performance.}}
\label{fig:HR_timecourse}
  \end{figure}

\begin{figure}[p]
  \centering
  \includegraphics[width=0.75\textwidth]{figs/weighted_timecourse_sleep}
\caption{\textbf{History of sleep efficiency and duration weighted by
    behavioral performance.}}
\label{fig:sleep_timecourse}
\end{figure}

\begin{sidewaysfigure}[p]
  \centering
  \includegraphics[width=0.75\textwidth]{figs/weighted_timecourse_activity_MH}
\caption{\textbf{History of fitness activity levels weighted by
    mental health factors.}}
\label{fig:activity_timecourse_MH}
\end{sidewaysfigure}

\begin{sidewaysfigure}[p]
  \centering
  \includegraphics[width=\textwidth]{figs/weighted_timecourse_HR_MH}
\caption{\textbf{History of cardiovascular activity weighted by
    mental health factors.}}
\label{fig:HR_timecourse_MH}
  \end{sidewaysfigure}

\begin{figure}[p]
  \centering
  \includegraphics[width=0.75\textwidth]{figs/weighted_timecourse_sleep_MH}
\caption{\textbf{History of sleep efficiency and duration weighted by
    mental health factors.}}
\label{fig:sleep_timecourse_MH}
  \end{figure}
